\documentclass{res}

\usepackage[margin=0.5in]{geometry}
\setlength{\textwidth}{7in}

\usepackage{xcolor}
\usepackage[normalem]{ulem}
\usepackage{hyperref}
\hypersetup{colorlinks,urlcolor=blue}

\makeatletter
\DeclareUrlCommand\ULurl@@{
  \def\UrlFont{\ttfamily\color{blue}}
  \def\UrlLeft{\uline\bgroup}
  \def\UrlRight{\egroup}}
\def\ULurl@#1{\hyper@linkurl{\ULurl@@{#1}}{#1}}
\DeclareRobustCommand*\ULurl{\hyper@normalise\ULurl@}
\makeatother

\newcommand*{\its}{\hspace{0.8cm}}

\begin{document}

\moveleft.5\hoffset\centerline{\Huge\bf Tejas Manohar}
\bigskip
\moveleft.5\hoffset\centerline{+1 (615) 974-7843\its{}me@tejas.io\its{}\its{}tejas.io\its{}linkedin.com/in/tejasmanohar\its{}github.com/tejasmanohar}

\section{SKILLS}

\begin{itemize} \itemsep -2pt
  \item HTML/CSS, Java, JavaScript, PHP, Python, Ruby
  \item AngularJS, Git, \LaTeX, Meteor, MongoDB, *nix, Node.js, Redis, Sinatra, SQL, Rails, Vim
\end{itemize}

\section{WORK EXPERIENCE}

{\bf Technical Writer}, Orchestrate \hfill November 2014 -- Present
\begin{itemize} \itemsep -2pt
  \item Writing how-tos on application development using Orchestrate's REST API w/ various technologies.
\end{itemize}

{\bf Regional Manager}, StudentRND \hfill July 2014 -- Present
\begin{itemize} \itemsep -2pt
  \item Arranging venues, food, qsponsorship, volunteers, etc. for CodeDay Nashville and St. Louis.
\end{itemize}

{\bf Creative Developer}, Chopdawg Studios \hfill September 2014 -- December 2014
\begin{itemize} \itemsep -2pt
  \item Working with entrepreneurs who have incredible ideas but require the technical resources to make it happen.
\end{itemize}

{\bf Software Engineer Intern}, Populr \hfill May 2014 -- August 2014
\begin{itemize} \itemsep -2pt
  \item Developed spam-detection mechanism to prevent script-invoked page creation.
  \item Implemented caching, compression, and load balancing with Varnish, Gzip, and HAProxy.
  \item Improved browser compatibility among older versions of IE for enterprise clients.
\end{itemize}

\section{SIDE PROJECTS}

\textbf{Quiztionary} -- Crowdsourced online dictionary powered by Quizlet.

\textbf{Twilio Plays 2048} -- Multiplayer 2048 based on SMS rather than IP; won Twilio award at Hack the North; featured in TechCrunch.

\textbf{Craigs Yo} -- Sends a Yo when your Craigslist search has a new listing; completed as contract work for Yo itself.

\textbf{Math Rounds} -- Mobile game operated via computing expressions rather than standard controls.

\textbf{iTNerary} -- Web app to help Nashville tourists build routed itineraries using Metro APIs.

\textbf{EdAllies} -- Academic social network revolving around P2P learning via student-initiated discussion.

\textbf{Art Attack} -- Mobile app for teaching and testing knowledge of important artwork in WCS art history courses.

\textbf{Sabercash} -- Intranet application to replace printed fake currency for middle school's behavior incentive program.

\section{HONORS}

\begin{itemize} \itemsep -2pt
  \item KPCB Fellows Semifinalist
  \item Best Use of Twilio at Hack the North
  \item Featured Student in Code.org
  \item 2nd at Hack for Change Nashville '14
  \item 1st at CodeDay St. Louis Spring '14
  \item MTSU Blue Spark Award
\end{itemize}

\section{EDUCATION}

Ravenwood High School, 2013 -- 2017 \textit {(expected)}

\section{ACTIVITIES}

\begin{itemize} \itemsep -2pt
  \item 2014 -- Present -- \textbf{Hackathons}, including PennApps X, Hack the North, MHacks V
  \item 2014 -- Present -- \textbf{Evangelist} of CodeDay Nashville, Nashville's first student hackathon
  \item 2013 -- Present -- \textbf{President} of Technology Club
  \item 2013 -- Present -- \textbf{Academic olympiads}, including Informatics, Linguistics, and Science
\end{itemize}

\end{document}
